\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-20 coq-example.tex
The Parser Example.

To prove \mintinline{Coq}{forall s, (is_prog s) + (is_prog s -> False)}, we use strong induction on the length and the non-trivial part is at the inductive step, i.e. we need to show \mintinline{Coq}{(forall e, len e < len s -> (is_prog e) + (is_prog e -> False)) -> (is_prog s) + (is_prog s -> False)}.

>>>>

\begin{figure}[!htb]
  \lstset{
      basicstyle=\fontsize{8}{8.5}\ttfamily,
  % numbers=left,
  }

  \begin{minipage}{\textwidth}
  \begin{multicols}{2}

  \definecolor{codecomment-color}{HTML}{0DA3FF}

  \begin{lstlisting}
  FInductive is_prog : strs -> Type := 
  | ip_seq : forall a b, is_prog a -> is_prog b 
      -> is_prog (a ++ [";"] ++ b) 
  | ip_assign : forall i e, is_atom i -> is_exp e 
      -> is_prog ([i; "="] ++ e).  
  \end{lstlisting}

  % \makeline[0pt]{Parser-exmp-before-start}{Parser-exmp-before-end}[codecomment-color!50]

  \columnbreak
  \definecolor{codecomment-color}{HTML}{5D030F}

  \begin{lstlisting}
  FInductive is_prog : strs -> Type += 
  | ip_if : forall a b, is_exp a -> is_prog b 
      -> is_prog (["if"] ++ a ++ ["then"] ++ b). 
  \end{lstlisting}

  % \makeline[.5\textwidth+9pt]{Parser-exmp-after-start}{Parser-exmp-after-end}[codecomment-color!50]

  \end{multicols}
  \end{minipage}
  \caption{"is_prog" and its extension}
  \end{figure}

To prove \mintinline{Coq}{forall s, (is_prog s) + (is_prog s -> False)}, we use strong induction on the length and the non-trivial part is  the inductive step, i.e. we need to show
\begin{minted}[fontsize=\footnotesize]{Coq}
  (forall e, len e < len s -> (is_prog e) + (is_prog e -> False)) -> (is_prog s) + (is_prog s -> False)
\end{minted}
